---
title: "Data_Incubator_PV"
author: "Brandon Burd"
date: "July 23, 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "Residential PV Adoption at Individual Level"
output:
  html_document: rmarkdown::github_document
---

#Load required packages
```{r load-packages, message=FALSE}
library(statsr)
library(dplyr)
library(ggplot2)
library(readr)
library(readxl)
library(haven)
library(broom)
library(QuantPsyc)
```






#IMPORT DATASETS


#Import raw PV installation data from Open PV Project
```{r open-raw-pv-data}
OpenPV_Raw <- read_csv("./openpv_all.csv")
```


#Import LCV (League of Conservation Voters) data with six expected errors
```{r open-LCV}
LCV_Data <- read_csv("./Master_LCV_Data_1980_2016.csv")
```


#Import master zip code list with voter district matches from Census
```{r open-voter-district-zip}
District_Zip <- read_excel("./District_Zip.xlsx")
```


#Import solar irradiance data from PV Watts (Lawrence Berkeley Labs)
```{r open-solar}
Solar_Data <- read_dta("./solar.dta")
```


#Import compiled electricity data from Energy Information Administration
```{r open-granular-elec}
Granular_Elec <- read_excel("./Granular_Electricity.xlsx")
```


#Import presidential voter data with interpolated years from Partisan Voter Index
```{r open-pres-vote}
Pres_Vote <- read_excel("./Political_Party.xlsx")
```


#Import median income data from Census in text format to retain leading zeroes (expected errors)
```{r open-median-income}
Income <- read_excel("./Median_Income.xlsx")
```


#Import land area data by county from Census
```{r open-land-area}
Area <- read_excel("./Land_Area.xls")
```


#Import pops and household size data from Census
```{r open-pops-and-households}
Pops <- read_excel("./Master_Pops.xlsx")
```


#Import master GeoID matcher, Zip <- makes GeoID matches
```{r open-fips-zips}
GeoID <- read_excel("./FIPS_Zips.xlsx")
```


#Import county to zips matcher
```{r open-county-zips}
County_Zips <- read_excel("./County_Zips.xlsx")
```


#Import state abbreviation matcher
```{r open-state-abbrev}
State_Abbreviations_Matcher <- read_excel("./State_Abbreviations_Matcher.xlsx")
```






#BUILD INDIVIDUAL-LEVEL MODEL FOR ANALYSIS


#Move clean, raw data to new df for relevant categories
```{r clean-raw-data}
Individual_Model <- OpenPV_Raw[, c(1,2,5,7,8,10,11,14,15,18,21,22)]
remove(OpenPV_Raw)
```


#Make rebate per kW variable in model
```{r rebate-per-kw-model}
Individual_Model$rebate_per_kW <- Individual_Model$rebate / Individual_Model$size_kw / 1000
```


#Make tax rate variable in model (NAs introduced for entries without tax information provided)
```{r tax-rate-model}
Individual_Model$Tax_Rate <- as.numeric(Individual_Model$sales_tax_cost) / as.numeric(Individual_Model$cost)
```


#Attach GeoID to model
```{r attach-geoid-model}
Individual_Model <- Individual_Model %>%
  mutate(GeoID = GeoID$GEOID[match(Individual_Model$zipcode, GeoID$ZIP, nomatch = NA)])
```


#Attach median income to model
```{r attach-median-income-model}
Individual_Model <- Individual_Model %>%
  mutate(Median_Income = Income$`Median Household Income`[match(Individual_Model$GeoID, Income$GeoID, nomatch = NA)])
```


#Attach land area to model
```{r attach-land-area-Model}
Individual_Model <- Individual_Model %>%
  mutate(Area = Area$`Land Area`[match(Individual_Model$GeoID, Area$GeoID, nomatch = NA)])
```


#Attach pops to model
```{r attach-pops-model}
Individual_Model <- Individual_Model %>%
  mutate(Pops = Pops$Population[match(Individual_Model$GeoID, Pops$GeoID, nomatch = NA)])
```


#Attach full state names to model
```{r attach-state-names-model}
Individual_Model <- Individual_Model %>%
  mutate(State = State_Abbreviations_Matcher$State[match(Individual_Model$state, State_Abbreviations_Matcher$Abbreviation, nomatch = NA)])
```


#Attach GeoID to District_Zip
```{r attach-geoid-district_zip}
District_Zip <- District_Zip %>%
  mutate(GeoID = GeoID$GEOID[match(District_Zip$Zip, GeoID$ZIP, nomatch = NA)])
```


#Attach voter district to model
```{r attach-district-model}
Individual_Model <- Individual_Model %>%
  mutate(District = District_Zip$District[match(Individual_Model$GeoID, District_Zip$GeoID, nomatch = 1)])
```


#Extract year from date in entries of model
```{r create-year-variable-model}
Individual_Model$Year <- substring(Individual_Model$date_installed,7,10)
```


#Make DistrictStateYear in model to match data
```{r district-state-year-model}
Individual_Model$DistrictStateYear <- paste(Individual_Model$District, Individual_Model$State, Individual_Model$Year, sep="")
```


#Make DistrictStateYear in LCV data to match data
```{r district-state-year-LCV}
LCV_Data$DistrictStateYear <- paste(LCV_Data$District, LCV_Data$State, LCV_Data$Year, sep="")
```


#Attach LCV scores to model
```{r attach-LCV-model}
Individual_Model <- Individual_Model %>%
  mutate(LCV = LCV_Data$Score[match(Individual_Model$DistrictStateYear, LCV_Data$DistrictStateYear)])
```


#Make StateYear in model
```{r state-year-column-model}
Individual_Model$StateYear <- paste(Individual_Model$State, Individual_Model$Year, sep="")
```


#Attach presidential voting data to model from Partisan Voter Index
```{r pres-vote-model}
Individual_Model <- Individual_Model %>%
  mutate(Pres_Vote = Pres_Vote$`%_Dem`[match(Individual_Model$StateYear, Pres_Vote$StateYear)])
```


#Attach solar radiation data to model (this is at State level I would like to get it by zip code if possible)
```{r attach-solar-model}
Individual_Model <- Individual_Model %>%
  mutate(Sol_Radiation = Solar_Data$Irradiance_m2[match(Individual_Model$State, Solar_Data$Full_Name)])
```


#Tag residential observations in model
```{r res-installs-labels-model}
Individual_Model <- Individual_Model %>%
  mutate(Residential = ifelse(grepl("residential|Residential|Residential/SF", Individual_Model$install_type), "Residential", "Not Residential"))
```


#Make YearGeoID in model
```{r year-geoid-model}
Individual_Model$YearGeoID <- paste(Individual_Model$Year, Individual_Model$GeoID, sep="")
```


#Attach granular electricity price data to model
```{r pull-gran-elec-price-model}
Individual_Model <- Individual_Model %>%
  mutate(Elec_Price = Granular_Elec$Price[match(Individual_Model$YearGeoID, Granular_Elec$YearGeoID, nomatch = NA)])
```


#Clean zeros from electricity price in model
```{r clean-gran-elec-price-model}
Individual_Model <- Individual_Model %>%
  mutate(Clean_Elec_Price = ifelse(Individual_Model$Elec_Price == 0, NA, Individual_Model$Elec_Price))
```


#Make filtered df with residential installs only
```{r res-filter}
Res <- Individual_Model[which(Individual_Model$Residential == "Residential"),]
```


#PLOT CHART 1



#Scatter plot install size by rebate 
```{r scatter-rebate-size}
ggplot(Res, aes(x = rebate, y = size_kw)) +
  geom_point() +
  coord_cartesian(ylim = c(0, 1500)) +
  stat_smooth(method = "lm", se = FALSE, color = "blue")
```
